\vskip-0.6in \Large Political Uncertainty

### 2015-04-24 GS-extension.tex
add SOC; shows solution is an inflection point

			The two symmetric conditions would be:
			\begin{multline}
					\Phi\left(- \alpha + b(0) \right)+  \Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right) 
					- 2 \Phi\left(- \alpha + b(0) \right)\Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right) \\ = \frac{\sqrt{2\pi}}{W_B \: e^{- \frac{\left(\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)\right)^2}{2}} }
				\end{multline}
			\begin{multline}
					\Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right)+  \Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) 
					- 2 \Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2})\right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right)\\ = \frac{\sqrt{2\pi}}{W_B \: e^{- \frac{\left( - \alpha + b\left(0\right)\right)^2}{2}} }
				\end{multline}
		\end{itemize}
	\item Some notes
		\begin{itemize}
			\item If we divide through by 2, the left side is the average minus the product
			\item If that is set equal to zero, the only solutions (for just one equation) are at (0,0) and (1,1). The right hand side modifies that.
			\item Need to check SOC at some point
			\item Remember, I'm ignoring the constraints on WTP and non-negativity of bribes
			\item First I'm going to try to get closed form answer / intuition by substituting logistic for normal CDF/PDF
		\end{itemize}
	\item Substituting logistic for normal in Equation~\ref{eq:firstfoc}
		\begin{equation}
					\frac{e^{- \alpha + b(0)}}{1+e^{- \alpha + b(0)}} + \frac{e^{\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)}}{1+e^{\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right) }}
					- 2\frac{e^{- \alpha + b(0)}}{1+e^{- \alpha + b(0)}}  \frac{e^{\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right) }}{1+e^{\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right) }} = \frac{\left(1+e^{-\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right)}\right)^2}{W_B \: e^{-\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right)} }
					\label{eq:logistic}
				\end{equation}
		\begin{itemize}
			\item A LOT of math (I will put it somewhere else) leads to three equations:
				\[
				  \left[ - \alpha + b(0) \right] = \left[ \frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right) \right] + \left[ -\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right) \right]
				\]
				\[
				   \left[ \frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right) \right] =\left[ - \alpha + b(0) \right]+ \left[ -\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right) \right]
				\]
				\[
				   \left[ -\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right) \right] = \left[ \frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right) \right] +\left[ - \alpha + b(0) \right]
				\]
			\item A little more math implies that all three quantities in brackets must equal zero
				\begin{itemize}
					\item That is, Vote Buyer B's bribe should make each legislator just indifferent between the new proposal and the status quo
					\item First question: why doesn't this depend on willingness-to-pay?
						\begin{itemize}
							\item FOC says each bribe should be calibrated so that $W_B \cdot \text{marginal contribution to probability} = 1$, or $\frac{\partial \text{probability}}{\partial \text{bribe}} = \frac{1}{W_B}$
							\item Something happens when all three conditions come together...what's the intuition?
						\end{itemize}
					\item To do next: see what non-negativity of bribes implies
						\begin{itemize}
							\item Also, insert Vote Buyer A's behavior
							\item And give the various legislators different variances
						\end{itemize}
				\end{itemize}
		\end{itemize}
\end{itemize}

\newpage
The math that follows from Equation \ref{eq:logistic}:
\begin{itemize}
	\item Let
		\begin{enumerate}
			\item $ X - \alpha + b(0)$ 
			\item $Y = \frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)$
			\item $Z = -\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right)$
		\end{enumerate}
	\item Then Equation \ref{eq:logistic} is equivalent to:
		\begin{equation}
			\frac{e^{X}}{1+e^{X}} + \frac{e^{Y}}{1+e^{Y }} - 2\frac{e^{X}}{1+e^{X}}  \frac{e^{Y }}{1+e^{Y }} = \frac{\left(1+e^{Z}\right)^2}{W_B \: e^{Z} }
					\label{eq:logistic2}
		\end{equation}
		\[
			\frac{e^{X} + 2e^{X+Y} + e^{Y}}{\left(1+e^{X}\right)\left(1+e^{Y }\right)} - 2\frac{e^{X+Y}}{\left(1+e^{X}\right)\left(1+e^{Y }\right)} = \frac{\left(1+e^{Z}\right)^2}{W_B \: e^{Z} }
		\]
		\[
			\frac{e^{X} + e^{Y}}{\left(1+e^{X}\right)\left(1+e^{Y }\right)} = \frac{\left(1+e^{Z}\right)^2}{W_B \: e^{Z} }
		\]
		\begin{equation}
			\frac{e^{X} + e^{Y}}{\left(1+e^{X}\right)\left(1+e^{Y }\right)} \frac{e^{Z}}{\left(1+e^{Z}\right)^2}= \frac{1}{W_B}
		\end{equation}
		Likewise, we have
		\begin{equation}
			\frac{e^{X} + e^{Z}}{\left(1+e^{X}\right)\left(1+e^{Z}\right)} \frac{e^{Y}}{\left(1+e^{Y}\right)^2}= \frac{1}{W_B}
		\end{equation}
		Setting the left-hand size of these two equations equal to each other,
		\[
		  \frac{e^{X} + e^{Y}}{\left(1+e^{X}\right)\left(1+e^{Y }\right)} \frac{e^{Z}}{\left(1+e^{Z}\right)^2}= \frac{e^{X} + e^{Z}}{\left(1+e^{X}\right)\left(1+e^{Z}\right)} \frac{e^{Y}}{\left(1+e^{Y}\right)^2}
		\]
		\[
		  \frac{e^{X+Z} + e^{Y+Z}}{1+e^{Z}}= \frac{e^{X+Y} + e^{Y+Z}}{1+e^{Y}}
		\]
		\[
		  e^{X+Z} + e^{Y+Z} + e^{X+Y+Z} +e^{2Y+Z}= e^{X+Y} + e^{Y+Z} + e^{X+Y+Z} +e^{Y+2Z}
		\]
		\[
		  e^{X+Z} +e^{2Y+Z}= e^{X+Y} +e^{Y+2Z}
		\]
		\[
		  e^{X}\left(e^{Z} - e^{Y} \right) = e^{Y+Z}\left(e^{Z} - e^{Y} \right)
		\]
		\[
		  e^{X} = e^{Y+Z}
		\]
		\begin{equation}
		  X = Y+Z
			\label{eq:X}
		\end{equation}
		By symmetry, we also have
		\begin{equation}
		  Y = X + Z
			\label{eq:Y}
		\end{equation}
		\begin{equation}
		  Z = X + Y
			\label{eq:Z}
		\end{equation}
		Substituting Equation \ref{eq:Z} into Equation \ref{eq:X}
		\[
		  X = Y + X + Y = X = 2Y \Rightarrow Y = 0
		\]
		Substituting from $Y = 0$ into Equation \ref{eq:X}, we have $X = Z$. Substituting both into Equation \ref{eq:Y}, we have $0 = Z + Z$, which implies $Z = 0$. Likewise for $X$. Thus we must have
		\[
		  X = Y = Z = 0
		\]		
\end{itemize}

>>>>

			The two symmetric conditions would be:
			\begin{multline}
					\Phi\left(- \alpha + b(0) \right)+  \Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right) 
					- 2 \Phi\left(- \alpha + b(0) \right)\Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right) \\ = \frac{\sqrt{2\pi}}{W_B \: e^{- \frac{\left(\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)\right)^2}{2}} }
				\end{multline}
			\begin{multline}
					\Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right)+  \Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) 
					- 2 \Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2})\right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right)\\ = \frac{\sqrt{2\pi}}{W_B \: e^{- \frac{\left( - \alpha + b\left(0\right)\right)^2}{2}} }
				\end{multline}
		\end{itemize}
	\item Some notes
		\begin{itemize}
			\item If we divide through by 2, the left side is the average minus the product
			\item If that is set equal to zero, the only solutions (for just one equation) are at (0,0) and (1,1). The right hand side modifies that.
			\item Need to check SOC at some point
			\item Remember, I'm ignoring the constraints on WTP and non-negativity of bribes
			\item First I'm going to try to get closed form answer / intuition by substituting logistic for normal CDF/PDF
		\end{itemize}
	\item Substituting logistic for normal in Equation~\ref{eq:firstfoc}
		\begin{equation}
					\frac{1}{1+e^{\alpha - b(0)}} + \frac{1}{1+e^{-\frac{\beta}{2} + \alpha - b\left(\frac{1}{2}\right) }}
					- 2\frac{1}{1+e^{\alpha - b(0)}}  \frac{1}{1+e^{-\frac{\beta}{2} + \alpha - b\left(\frac{1}{2}\right) }} = \frac{\left(1+e^{\frac{\beta}{2} + \alpha - b\left(-\frac{1}{2}\right)}\right)^2}{W_B \: e^{\frac{\beta}{2} + \alpha - b\left(-\frac{1}{2}\right)} }
					\label{eq:logistic}
				\end{equation}
		\begin{itemize}
			\item A LOT of math (I will put it somewhere else) leads to three equations:
				\[
				  \left[ - \alpha + b(0) \right] = \left[ \frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right) \right] + \left[ -\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right) \right]
				\]
				\[
				   \left[ \frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right) \right] =\left[ - \alpha + b(0) \right]+ \left[ -\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right) \right]
				\]
				\[
				   \left[ -\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right) \right] = \left[ \frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right) \right] +\left[ - \alpha + b(0) \right]
				\]
			\item A little more math implies that all three quantities in brackets must equal zero
				\begin{itemize}
					\item That is, Vote Buyer B's bribe should make each legislator just indifferent between the new proposal and the status quo
					\item First question: why doesn't this depend on willingness-to-pay?
						\begin{itemize}
							\item FOC says each bribe should be calibrated so that $W_B \cdot \text{marginal contribution to probability} = 1$, or $\frac{\partial \text{probability}}{\partial \text{bribe}} = \frac{1}{W_B}$
							\item Something happens when all three conditions come together...what's the intuition?
						\end{itemize}
					\item To do next: see what non-negativity of bribes implies
						\begin{itemize}
							\item Also, insert Vote Buyer A's behavior
							\item And give the various legislators different variances
						\end{itemize}
				\end{itemize}
		\end{itemize}
\end{itemize}

\newpage
The math that follows from Equation \ref{eq:logistic}:
\begin{itemize}
	\item Let
		\begin{enumerate}
			\item $X = -\alpha + b(0)$ 
			\item $Y = \frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)$
			\item $Z = -\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right)$
		\end{enumerate}
	\item Then Equation \ref{eq:logistic} is equivalent to:
		\begin{equation}
			\frac{1}{1+e^{-X}} + \frac{1}{1+e^{-Y}} - 2\frac{1}{1+e^{-X}}  \frac{1}{1+e^{-Y}} = \frac{\left(1+e^{-Z}\right)^2}{W_B \: e^{-Z} }
					\label{eq:logistic2}
		\end{equation}
		\[
			\frac{2 + e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} - 2\frac{1}{1+e^{-X}}  \frac{1}{1+e^{-Y}} = \frac{\left(1+e^{-Z}\right)^2}{W_B \: e^{-Z}}
		\]
		\[
			\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} = \frac{\left(1+e^{-Z}\right)^2}{W_B \: e^{-Z}}
		\]
		\begin{equation}
			\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \frac{e^{-Z}}{\left(1+e^{-Z}\right)^2}= \frac{1}{W_B}
		\end{equation}
		Likewise, we have
		\begin{equation}
			\frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}= \frac{1}{W_B}
		\end{equation}
		Setting the left-hand size of these two equations equal to each other,
		\[
		  \frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \frac{e^{-Z}}{\left(1+e^{-Z}\right)^2}= \frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}
		\]
		\[
		  \frac{e^{-X-Z} + e^{-Y-Z}}{1+e^{-Z}}= \frac{e^{-X-Y} + e^{-Y-Z}}{1+e^{-Y}}
		\]
		\[
		  e^{-X-Z} + e^{-Y-Z} + e^{-X-Y-Z} +e^{-2Y-Z}= e^{-X-Y} + e^{-Y-Z} + e^{-X-Y-Z} +e^{-Y-2Z}
		\]
		\[
		  e^{-X-Z} +e^{-2Y-Z}= e^{-X-Y} +e^{-Y-2Z}
		\]
		\[
		  e^{-X}\left(e^{-Z} - e^{-Y} \right) = e^{-Y-Z}\left(e^{-Z} - e^{-Y} \right)
		\]
		\[
		  e^{-X} = e^{-Y-Z}
		\]
		\begin{equation}
		  -X = -Y-Z
			\label{eq:X}
		\end{equation}
		By symmetry, we also have
		\begin{equation}
		  -Y = -X - Z
			\label{eq:Y}
		\end{equation}
		\begin{equation}
		  -Z = -X - Y
			\label{eq:Z}
		\end{equation}
		Substituting Equation \ref{eq:Z} into Equation \ref{eq:X}
		\[
		  - X = - Y - X - Y \Rightarrow 0 = 2Y \Rightarrow Y = 0
		\]
		Substituting from $Y = 0$ into Equation \ref{eq:X}, we have $X = Z$. Substituting both into Equation \ref{eq:Y}, we have $0 = Z + Z$, which implies $Z = 0$. Likewise for $X$. Thus we must have
		\[
		  X = Y = Z = 0
		\]		
\end{itemize}

\vskip1in
Perhaps more importantly, let's look at the second order condition (using the same substitutions at the top of the previous page). The first derivative of the objective function w.r.t. $b(-\frac{1}{2})$ is (in logistic form)
\[
  W_B\frac{e^{-Z}}{\left(1+e^{-Z}\right)^2}\left[\frac{1}{1+e^{-X}} + \frac{1}{1+e^{-Y}} - 2\frac{1}{1+e^{-X}}  \frac{1}{1+e^{-Y}} \right] - 1
\]
\[
  W_B\frac{e^{-Z}}{\left(1+e^{-Z}\right)^2}\left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] - 1
\]
Now, the second derivative:
\[
  W_B\left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] \left[ \frac{e^{-Z} 2\left(1+e^{-Z}\right) e^{-Z}-\left(1+e^{-Z}\right)^2 e^{-Z}}{\left(1+e^{-Z}\right)^4} \right]
\]
\[
  W_B\left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] \left[ \frac{e^{-Z} 2 e^{-Z}-\left(1+e^{-Z}\right) e^{-Z}}{\left(1+e^{-Z}\right)^3} \right]
\]
\[
  W_B\left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] \left[ \frac{e^{-Z} \left\{2 e^{-Z}-\left(1+e^{-Z}\right) \right\}}{\left(1+e^{-Z}\right)^3} \right]
\]
\[
  W_B\left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] \left[ \frac{e^{-Z} \left\{2 e^{-Z}-1-e^{-Z} \right\}}{\left(1+e^{-Z}\right)^3} \right]
\]
\[
  W_B\left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] \left[ \frac{e^{-Z} \left\{e^{-Z}-1 \right\}}{\left(1+e^{-Z}\right)^3} \right]
\]
\[
  W_B\left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] \left[ \frac{e^{-Z}}{\left(1+e^{-Z}\right)^3} \right] \left\{e^{-Z}-1 \right\}
\]
Everything except for the expression in the curly braces is positive. The expression in the curly braces is positive when $z\leq0$ and negative when $z\geq0$. So this objective function appears to have an inflection point at $z=0$.
